\addcontentsline{toc}{section}{Abstract}
\section*{Abstract}

\begin{textblock}
Autonomous boat navigation has demonstrated significant potential for applications in maritime transportation, water and environmental analysis, search and rescue operations, and scientific exploration. The primary objective of this project is to develop a versatile and robust simulation environment that can serve as a Digital Twin for testing safely and efficiently autonomous navigation systems for boats. 

Deep Reinforcement Learning (DRL) techniques have emerged as highly effective approaches for training autonomous agents in complex and unpredictable environments, which involve precise, otherwise potentially critical, machine-human, machine-environment, or machine-machine interactions, such as self-driving cars, kitchens, agriculture, and production lines.

Simulated environments and digital twins have become crucial in developing autonomous robotics solutions for real-life critical applications. They significantly reduce training costs and time, making the process more affordable, efficient, and reproducible. This project aims to provide a comprehensive framework for developing and verifying DRL and Safe DRL techniques. It includes a ready-to-use physical simulation of water, waves, and obstacles, specifically designed for the port of the city of Garda. Additionally, the project offers Python code for training the autonomous agent, both with and without safety constraints. It also provides all the necessary assets, tools, and instructions for easily customizing the simulator to different real-world locations.

By focusing on the development of a realistic physical interaction between water, boat geometries, and sensor responses in various weather conditions, this project lays the foundations for training boats to perform complex tasks. Although the experiments in this study are limited to simple way-point navigation using GPS coordinates, they serve as a starting point for future endeavours involving multi-agent environments, pollutant source tracing, and intricate obstacle avoidance scenarios.
\end{textblock}



\blankpage